Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-14 chapters/final_remarks.tex
Fixed some captions for figures

Building on the observed coupling between interfacial particle dynamics and bijel microstructure, we propose extending 
this work by investigating bijels stabilized with non-rigid, cohesive, or attractive particles. Unlike rigid ellipsoids, 
soft and cohesive particles are known to exhibit distinct glass transition behaviors and rheological responses compared 
to hard-sphere systems \cite{weeks_introduction_2017, torquato_jammed_2010}. In bijel architectures, attractive interactions have been 
proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic 
applications \cite{boakye-ansah_controlling_2020}. 
Similarly, soft particles such as nanogels and hydrogels have attracted interest in biomedical contexts, offering tunable responsiveness 
to environmental stimuli like temperature and pH—critical features for controlled drug delivery. Incorporating such particles 
could alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 
explored computationally using Lattice Boltzmann Methods integrated with immersed boundary method based frameworks to account for
particle deformation or attractive particle interactions to account for electrostatic cohesion \cite{silva_lattice_2024}. This direction opens opportunities 
to design bijel systems with enhanced adaptability and function, tailored for application-specific demands.

>>>>

Building on the observed coupling between interfacial particle dynamics and bijel microstructure, we propose extending 
this work by investigating bijels stabilized with non-rigid, cohesive, or attractive particles. Unlike rigid ellipsoids, 
soft and cohesive particles are known to exhibit distinct glass transition behaviors and rheological responses compared 
to rigid-sphere systems \cite{weeks_introduction_2017, torquato_jammed_2010}. In bijel architectures, attractive interactions have been 
proposed as a strategy to form “armored” interfaces, potentially enhancing mechanical integrity and enabling higher flow rates in catalytic 
applications \cite{boakye-ansah_controlling_2020}. 
Similarly, soft particles such as nanogels and hydrogels have attracted interest in biomedical contexts, offering tunable responsiveness 
to environmental stimuli like temperature and pH for controlled drug release applications for example \cite{thorson_bijel-templated_2019, vanoli_bijels_2022}. 
Incorporating such particles 
could alter jamming dynamics, interfacial rearrangement, and field-induced responsiveness. These effects may be 
explored computationally using Lattice Boltzmann Methods integrated with immersed boundary method based frameworks to account for
particle deformation or attractive particle interactions to account for electrostatic cohesion \cite{silva_lattice_2024}. This direction opens opportunities 
to design bijel systems with enhanced adaptability and function, tailored for application-specific demands.

### 2025-04-14 chapters/paper2.tex
Fixed some captions for figures

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper2/nematic-field_on.png} 
    \caption{Evolution of the nematic order parameter \( S \) over time for bijels stabilized with disc-like particles (left) and rod-like particles (right), 
             after the application of varying magnetic field strengths.} 
    \label{fig:nematic-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_down.png} 
\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
         is switched off, along with a reduction in the ordering of the particles.} 
\label{fig:domain_size-field_down} 
\end{figure}

>>>>

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/nematic-field_on.png} 
    \caption{Evolution of the nematic order parameter \( S \) over time for bijels stabilized with disc-like particles (left) and rod-like particles (right), 
             after the application of varying magnetic field strengths.} 
    \label{fig:nematic-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_down.png} 
\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle plotted over time. 
         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
         is switched off.} 
\label{fig:domain_size-field_down} 
\end{figure}

### 2025-04-14 chapters/paper3.tex
Fixed some captions for figures

Particle ordering plays a critical role in determining the rheological behavior of suspensions, as aligned particles can more readily slide past one another 
under shear, delaying structural breakdown. In bijels, where particles are adsorbed at the fluid-fluid interface, this interfacial confinement may significantly 
influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with Herschel-Bulkley rheology, 
indicating a non-Newtonian response governed by both interfacial structure and particle dynamics \cite{macmillan_rheological_2019}. To investigate these effects in 
the presence of magnetic fields and varying degrees of particle ordering, we apply constant shear to the bijel templates and plot the resulting time evolution of 
the shear stress, as shown in Figure~\ref{fig:stress_time}.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/stress_strain-all.png} 
    \caption{Fitting the experimental shear stress to the strain rate using the Herschel-Bulkley model. We characterize the bijels are 
             shear thinning in all cases and that the bijels become less shear thinning as the particle order increases. We also
             demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
             prolate particles.} 
    \label{fig:stress_strain} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the orientation of particles to the applied shear is dependent on the
             applied shear rate, particle ordering to the field and the particle shape.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same. We show that the particles tilt out of the interface upon application of shear with the degree of
             interfacial tilting a function of the initial particle order and particle shape.} 
    \label{fig:interface_angle_shear} 
\end{figure}

@@

Comparing the trends in $\langle \psi \rangle$ and $\langle \theta_z \rangle$ reveals a complementary view of how shear flow governs particle reorientation in bijels. For systems 
stabilized with oblate particles under no magnetic field and prolate particles subjected to a magnetic field, the results show that at low shear rates, particles largely resist 
reorientation due to interfacial jamming and anchoring forces. However, as the shear rate increases, both $\langle \psi \rangle$ and $\langle \theta_z \rangle$ rise, indicating that 
particles begin to tilt away from both the interface normal and the shear direction. This suggests that while the particles remain adsorbed at the interface, the imposed shear is strong 
enough to overcome local resistance and drive reorientation. The resulting changes in local packing and alignment are reflected in variations in the bond-orientational order parameter 
$\langle Q6 \rangle$, particularly under conditions where the bijel retains structural integrity and resists complete flow-induced breakdown.

>>>>

Particle ordering is one factor that affects the rheological behavior of suspensions, as aligned particles reduce particle-fluid interactions, reducing the
induced shear stress. In bijels, where particles are adsorbed at the fluid-fluid interface, interfacial confinement may significantly 
influence the degree of slip and the onset of yielding. Prior studies have shown that bijels exhibit shear-thinning behavior consistent with the Herschel-Bulkley fluid model, 
indicating a non-Newtonian response governed by both interfacial structure and particle dynamics \cite{macmillan_rheological_2019}. To investigate these effects in 
the presence of magnetic fields and varying degrees of particle ordering, we apply constant shear to the bijel templates and plot the resulting time evolution of 
the shear stress, as shown in Figure~\ref{fig:stress_time}.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/stress_strain-all.png} 
    \caption{Fitting the experimental shear stress to the strain rate using the Herschel-Bulkley model for bijels stabilized by
             ellipsoidal particles with no magnetic field applied $\bar{B} = 0$ and an applied field of $\bar{B} = 1$ when starting at different
             initial microstructures.} 
    \label{fig:stress_strain} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/theta_z-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the direction of the applied shear for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same.} 
    \label{fig:theta_z_specific} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper3/psi-time_compare-specific.png} 
    \caption{Comparisons of the average orientation of particles to the interface for bijels stabilized by
             ellipsoidal particles as a function of the applied shear rate for bijels made with no field and a field strength of $\bar{B} = 1$,
             keeping the field strength the same during shear.} 
    \label{fig:interface_angle_shear} 
\end{figure}

@@

Comparing the trends in $\langle \psi \rangle$ and $\langle \theta_z \rangle$ reveals a complementary view of how shear flow governs particle reorientation in bijels. For systems 
stabilized with oblate particles under no magnetic field and prolate particles subjected to a magnetic field, the results show that at low shear rates, particles largely resist 
reorientation due to interfacial jamming and anchoring forces. However, as the shear rate increases, both $\langle \psi \rangle$ and $\langle \theta_z \rangle$ rise, indicating that 
particles begin to tilt away from both the interface normal and the shear direction. This suggests that while the particles remain adsorbed at the interface, the imposed shear is strong 
enough to overcome local resistance and drive reorientation. The resulting changes in local packing and alignment are reflected in variations in the bond-orientational order parameter 
$\langle Q6 \rangle$.
